Some Negativity Results for Moduli

### 2013-02-16 writeup/paper.tex
fixing numlangs table
table with counts of dictionaries

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
&\# languages&\# Turkers\\
\hline
No languages&0&2555\\\\
One language&1&2651\\\\
Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%% NUM LANGUAGES TABLE %%%%%%%%%%%
\begin{figure}[h]
\begin{tabular}{ccc}\hline\hline
IGNORE TABLE& WILL FIX SOON&\\
&\# languages&\# Turkers\\
\hline
No languages&0&2555\\\\
One language&1&2651\\\\
Multiple languages&2&684\\
&3&94\\
&4&23\\
&5&7\\
&6&8\\
&7&4\\
&8&1\\
&9&2\\
&10&3\\
&15&1\\
\hline\hline
\end{tabular}
\label{numlangs-tab}\\
\caption{Number of native languages reported during demographic survey.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% MISREPORT TABLE %%%%%%%%%%%
\begin{figure}[h]
\centering
\begin{tabular}{cccc}
Language&Total&Quality $\geq$ 0.5& Quality $>$ 0.5\\\hline\hline
af&9983.0&7199.0&1679.0\\
am&8341.0&6646.0&2489.0\\
an&3080.0&938.0&228.0\\
ar&9994.0&9638.0&5024.0\\
ast&9968.0&9035.0&3808.0\\
az&9975.0&7034.0&1983.0\\
bcl&9940.0&4718.0&384.0\\
be&9964.0&7008.0&2039.0\\
bg&9982.0&8389.0&2622.0\\
bn&9984.0&8915.0&3761.0\\
bo&9920.0&1744.0&64.0\\
bpy&9854.0&6439.0&2604.0\\
br&9978.0&6188.0&1722.0\\
bs&9860.0&7110.0&1913.0\\
ca&9993.0&7318.0&1533.0\\
ceb&9445.0&5394.0&1202.0\\
cs&9957.0&6844.0&1342.0\\
cy&9971.0&5369.0&942.0\\
da&9983.0&8827.0&2843.0\\
de&9921.0&8594.0&2609.0\\
diq&33.0&8.0&0\\
el&9994.0&8150.0&2630.0\\
eo&9962.0&7261.0&1574.0\\
es&9835.0&8127.0&2265.0\\
eu&9993.0&9031.0&3365.0\\
fa&5565.0&3527.0&1070.0\\
fi&9968.0&8527.0&2499.0\\
fr&9900.0&8472.0&2859.0\\
fy&9962.0&6840.0&1618.0\\
ga&9914.0&8421.0&2711.0\\
gl&9987.0&7843.0&2606.0\\
gu&9982.0&9916.0&9294.0\\
he&8271.0&5807.0&1854.0\\
hi&9949.0&9519.0&6066.0\\
hr&9949.0&8723.0&2589.0\\
ht&9938.0&8874.0&3323.0\\
hu&9885.0&8304.0&2246.0\\
hy&1758.0&1314.0&613.0\\
id&9770.0&7090.0&1363.0\\
ilo&9705.0&7510.0&1303.0\\
io&147.0&58.0&41.0\\
is&9913.0&6163.0&1907.0\\
it&9755.0&8270.0&2312.0\\
ja&8053.0&4204.0&1501.0\\
jv&9883.0&7126.0&1404.0\\
ka&5557.0&3837.0&1437.0\\
kk&40.0&8.0&8.0\\
kn&9993.0&9928.0&8591.0\\
\end{tabular}
\label{mism-tab}
\end{figure}
\clearpage
\begin{figure}[h]
\centering
\begin{tabular}{cccc}
ko&7159.0&3244.0&1094.0\\
ku&149.0&70.0&0\\
lb&9965.0&6786.0&1498.0\\
lt&9975.0&8044.0&2197.0\\
lv&9981.0&7343.0&2008.0\\
mg&201.0&46.0&5.0\\
mk&9845.0&9373.0&5138.0\\
ml&9991.0&9795.0&7047.0\\
mr&9993.0&9840.0&7540.0\\
ms&9766.0&8348.0&2810.0\\
nap&6540.0&2171.0&462.0\\
nds&7324.0&3179.0&615.0\\
ne&9972.0&9570.0&6100.0\\
new&9976.0&6530.0&1018.0\\
nl&9932.0&8924.0&3106.0\\
nn&9994.0&8355.0&2529.0\\
no&9941.0&8965.0&3070.0\\
pa&9881.0&9464.0&6611.0\\
pam&9909.0&6960.0&1384.0\\
pl&9813.0&7207.0&1367.0\\
pms&9285.0&4104.0&688.0\\
ps&9727.0&5309.0&794.0\\
pt&9857.0&7638.0&1554.0\\
qu&67.0&0&0\\
ro&9875.0&8849.0&2804.0\\
ru&9977.0&0&0\\
scn&9983.0&8446.0&3476.0\\
sd&9357.0&3866.0&139.0\\
sh&9930.0&8120.0&2043.0\\
sk&9977.0&6039.0&1435.0\\
sl&9889.0&5871.0&1092.0\\
so&9908.0&2925.0&263.0\\
sq&9924.0&8237.0&2468.0\\
sr&9890.0&9005.0&3428.0\\
su&9947.0&5818.0&891.0\\
sv&9856.0&8127.0&2241.0\\
sw&9770.0&8148.0&2186.0\\
ta&9979.0&9687.0&6948.0\\
te&9933.0&9085.0&5265.0\\
th&4252.0&2381.0&883.0\\
tl&9280.0&7173.0&2475.0\\
tr&9941.0&8011.0&1896.0\\
tt&40.0&8.0&8.0\\
uk&9787.0&6349.0&2208.0\\
ur&9864.0&3076.0&1033.0\\
uz&9874.0&6643.0&1122.0\\
vi&8276.0&7027.0&2935.0\\
wa&49.0&28.0&11.0\\
war&8579.0&5273.0&874.0\\
wo&9759.0&5691.0&0\\
yo&2367.0&2119.0&1245.0\\
zh&3647.0&2812.0&1037.0\\
\hline\hline
\end{tabular}
\label{mism-tab}
\caption{Quality of translations recieved from truthful versus misreporting Turkers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
